---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
# options(tibble.print_min = 4L, tibble.print_max = 4L)
library(dplyr)
# devtools::load_all("C:/Users/stern/Dropbox/sternclean")
library(sternclean)
library(pander)
set.seed(1014)
```


`sternclean` seeks to simplify cleaning dataframes as much as
possible.

Multiple cleaning steps can be done in just one function.

For example,
you can change column types, impute one set of columns' NAs with 
a set value, impute another set of columns' NAs with a group mean, and
impute another set of columns' infinite values with another set value
in a few lines of clean code

Here is the Order of operations under the hood: 


- Change the types
- Remove columns
- Impute NAs
- Impute infinites

This allows multiple cleaning processes to happen in this one function


## Simple Examples
We will start out with over simple one step cleaning steps. Later we will take on more complex situations

### Rickle and Mortan Dataset

```{r, echo = FALSE, message = FALSE, results = "asis"}

people <- c("Rickle", "Mortan", "Jerry", "Pickle Rickle")
original_person <- c("Rickle", "Mortan", "Jerry", "Rickle")
intelligence <- c(Inf, 9, 0.1, Inf)
evil_rank <- c(5, 2.75, 2, NA)

rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)


rickle_and_mortan$people <- as.factor(rickle_and_mortan$people)

pander::pandoc.table(rickle_and_mortan)

rickle_and_mortan$intelligence <- as.character(rickle_and_mortan$intelligence)
```

#### class change parameters
```{r}
class(rickle_and_mortan$people)

sternclean("rickle_and_mortan",
           class_to_strng = "people")

class(rickle_and_mortan$people)

```


```{r}
class(rickle_and_mortan$intelligence)

sternclean("rickle_and_mortan",
           class_to_numer = "intelligence")

class(rickle_and_mortan$intelligence)

```

#### column/row removal parameters

```{r}
sternclean("rickle_and_mortan",
           remove_columns = "intelligence")

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

```{r}
sternclean("rickle_and_mortan",
           remove_na_rows =  "evil_rank")

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

```{r}
sternclean("rickle_and_mortan",
           removeby_regex = "pe")

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

```{r}
sternclean("rickle_and_mortan",
           remove_all_nas = TRUE)

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

```{r}
sternclean("rickle_and_mortan",
           remove_non_num = TRUE)

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

```{r}
sternclean("rickle_and_mortan",
           remove_all_exc = c("people", "evil_rank"))

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

#### impute parameters

```{r}
sternclean("rickle_and_mortan",
           impute_na2mean = "evil_rank")

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```
```{r}
sternclean("rickle_and_mortan",
           impute_na_cols = "evil_rank",
           impute_na_with = 1738)

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

```{r}
sternclean("rickle_and_mortan",
           impute_grpmean = "evil_rank",
           impute_grpwith = "original_person")

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```
```{r}
sternclean("rickle_and_mortan",
           impute_inf_col = "intelligence",
           impute_inf_wit = 1738)

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```

```{r}
sternclean("rickle_and_mortan",
           impute_cust_cl = "evil_rank",
           impute_cust_fn = quantile,
           probs = .25,
           na.rm = TRUE
           )

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```


#### More complex example

Here we will:


- change the intelligence column type to numeric 
- change the people cloumn type to character 
- remove the original_person column 
- impute the evil_rank column's NAs with the column average
- impute the intelligence column with 1738
  

```{r}
sternclean("rickle_and_mortan",
           class_to_numer = "intelligence",
           class_to_strng = "people",
           remove_columns = "original_person",
           impute_na2mean = "evil_rank",
           impute_inf_col = "intelligence",
           impute_inf_wit =  1738
           
           )

```

```{r, results = "asis", echo=FALSE}
pander::pandoc.table(rickle_and_mortan)
rickle_and_mortan <- data.frame(people, original_person,
                                intelligence, evil_rank)

```



> "For more, checkout my "
([Github](https://github.com/basketballbeane))
